---
title: "Introduction to RUGtools"
author: "Justin M. Shea"
date: "June 8th, 2019"
output: html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{New Meetup Members}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)

library(RUGtools)
```

## Introduction



## R User Group Introduction Slides template

This is a traditional ioslides R Markdown template, but modified to contain default content routinely used when introducing Chicago R user group meetups.
Slides are useful because they look good and you won't forget to do important things
like **thanking the sponsors!** Slides can be accessed from within R Studio 
using the `New R Markdown` dialog menu, and then selecting `From Template`. 
One can also use the `draft` function, exemplified below.

```{r, eval=FALSE}
rmarkdown::draft(file="new_meetup.Rmd", template = "intro_slides", package="RUGtools")
```

## Estimate your pizza order

In Chicago, we think a lot about Pizza. And if one is involved in the local meetup 
culture, this is doubly so. At a recent meetup group that wasn't ours, I counted 
nearly 6 large pizzas left over. Struck by an overwhelming sorrow, I vowed the 
Chicago R User Group shall never partake in such a tragic waste of resources. 
With a few data points, one can use the `pizza_estimate` function to arrive at
a more efficient order.

```{r, align = "l"}
kable( pizza_estimate(registered = 120, pizza_diameter = 18, attend_rate = 0.57, 
                      serving = 2, style = "thin") )

```
 
Channeling our ever-curious pizza scientist, _**it turns out**_ the Chicago
"party cut" (thin-crust cut into small squares) inherits a few very attractive 
properties when dividing **n** pizzas among **p** guests. Small square pieces allow 
guests to better estimate pizza consumption, thus decreasing the integer-programming 
problem exacerbated by large triangular slices. Reducing wasted pizza is not only 
virtuous, it demonstrates great stewardship of sponsor resources bestowed upon thee.

```{r, echo=FALSE, fig.height= 6, fig.width= 6}
plot(3*c(1, 0, -1, 0), 3*c(0, 1, 0, -1) , col = "transparent",
     xaxs="i", yaxs="i", xaxt="n", yaxt="n", ylab="18 inches", xlab="18 inches", 
     main = "The Chicago `Party Cut` Extra-Large Pizza", bg = "white")
polygon(3*sin(seq(0, 2*pi, length=100)), 3*cos(seq(0, 2*pi, length=100)), border = "goldenrod1", lwd=14, col = "lightgoldenrod1")
points(x=jitter(c((1:4)-2.5, seq(from = -2, to =2, length.out=6), (1:6)-3.5, (1:6)-3.5, seq(from = -2, to =2, length.out=6), (1:4)-2.5), factor = 2), 
     y=jitter(c(rep(2.75,4), rep(1.85, 6), rep(1,6), rep(0,6), rep(-0.85, 6), rep(-1.75,4))-0.5, factor=1.33), pch=19, cex=4, col="red")
points(x=jitter(c((1:4)-2.5, seq(from = -2, to =2, length.out=6), (1:6)-3.5, (1:6)-3.5, seq(from = -2, to =2, length.out=6), (1:4)-2.5), factor = 2), 
     y=jitter(c(rep(2.75,4), rep(1.85, 6), rep(1,6), rep(0,6), rep(-0.85, 6), rep(-1.75,4))-0.5, factor=2), pch="`", cex=6, col="green")
points(x=jitter(c(seq(from=-1.5, to=1.5, length.out=12), seq(from = -2, to =2, length.out=18), seq(from=-3, to=3, length.out=24), seq(from=-3, to=3, length.out=24), seq(from = -2, to =2, length.out=18), seq(from=-1.5, to=1.5, length.out=12)), factor = 2), 
       y=jitter(c(rnorm(12, mean = 3, sd=0.5), rnorm(18, mean = 2, sd=0.5), rnorm(24, mean = 1, sd=0.5), rnorm(24, mean = 0, sd=0.5), rnorm(18, mean = -1, sd=0.5), rnorm(12, mean = -2, sd=0.5))-0.5, factor=2), pch=".", cex=1.5, col="black")
abline(h=-3:3, col="white", lwd=2.5)
abline(v=-3:3, col="white", lwd=2.5)
```
 


## Data Analysis

Chicago R User Group data is included and downloaded from meetup.com/ChicagoRUG.
Personally identifiable information has been removed, data formatted and ready for analysis.

Load the member list data. 
How many members do we have?

```{r}
nrow(member_list)
```

Lets plot the cumulative membership.

```{r, tidy=TRUE}
plot(y = member_list$Member.ID, x = member_list$Joined.Group.on, type = "l", lwd=2, 
     col = "blue", frame = FALSE, main = "Chicago R User Group members", 
     ylab = "Members", xlab = "", ylim = c(0, 4000), 
     xlim=c(min(member_list$Joined.Group.on), as.Date("2020-01-01")))
```

How many members joined since January 2017?

```{r}
nrow(subset(member_list, Joined.Group.on > "2017-01-01"))
```
What percentage of the Chicago R User Group joined since January 2017?

```{r}
Percentage <- 100 * NROW(subset(member_list, Joined.Group.on > "2017-01-01")) / NROW(member_list)
round(Percentage, 2)
```


## How many new members usually join between meetups? 

First, get a unique ordered list of Meetup dates

```{r}
Meetup_dates <- sort(unique(member_list$Last.Attended))

new_members <- subset(member_list, Joined.Group.on > Meetup_dates[NROW(Meetup_dates)])
```
 
Then count the number of new members joined between the most recent meetup and the one prior to that.

```{r}
new_members2 <- subset(member_list, Joined.Group.on <= Meetup_dates[NROW(Meetup_dates)] &
                                    Joined.Group.on > Meetup_dates[NROW(Meetup_dates)-1])

nrow(new_members2)
```

In danger of repeating the above analysis several times over, we created a function `new_mem_counter` to count the number of new members joined between meetups for 
all meetups in the data set.

```{r}
new_members <- new_mem_counter(member_list)
# drop the last observation, as incomplete data leading up to the coming meetup.
new_members <- new_members[-NROW(new_members),]

kable(head(new_members), align = 'l')

kable(tail(new_members), align = 'l')
```

Which gap between meetups had the most new members?
 
```{r}
kable(new_members[new_members$New==max(new_members$New), ], align = 'l')
```

Note the previous meetup was 6 months prior, so likely this was not due to the topic covered.

What is the average number of new members joined between meetups?
 
```{r, message=FALSE, warning=FALSE}
mean(new_members$New)
```

Plot the `new members` data.

```{r}
   # Create Date Range Index
  Date_Index <- as.numeric(row.names(new_members[new_members$Date > "2010-01-01" & new_members$Date <= Sys.Date(),]))
  
  # Create x-axis labels, using year-month date format
  x_labels <- format(new_members$Date[Date_Index], "%Y-%m")

  # Plot
  barplot(new_members$New[Date_Index], names.arg = x_labels, main = "CRUG members, joined between meetups",  
          ylab = "New Members", xlab = "")
```

Plot the `new members` data since 2017.

```{r}
   # Create Date Range Index
  Date_Index <- as.numeric(row.names(new_members[new_members$Date > "2017-01-01" & new_members$Date <= Sys.Date(),]))
  
  x_labels <- format(new_members$Date[Date_Index], "%Y-%m")

  # Plot
  barplot(new_members$New[Date_Index], names.arg = x_labels, las=2, main = "CRUG members, joined between meetups",  
          ylab = "New Members", xlab = "")
```
 
What is the average number of new members joined between meetups since 2017?
 
```{r, message=FALSE, warning=FALSE}
mean(new_members$New[Date_Index])
```


#  Membership as time series

Load and use the `xts` package.

```{r, message=FALSE, warning=FALSE}
library(xts)

members_xts <- xts(x = member_list$Member.ID, order.by = member_list$Joined.Group.on)
names(members_xts) <- "useRs"

plot(members_xts, col = "blue", grid.col = "white", main = "Chicago R User Group members by join date")
```

### How many members join by month?

```{r}
members_monthly <- to.monthly(members_xts, OHLC = FALSE)

barplot(diff(members_monthly), col = "lightgrey", main = "Chicago R User Group, new members by month")
```

### What's our percentage growth per month?

Omit the first two months growth outliers. 

```{r}
barplot(100*diff(members_monthly)[-c(1,2)]/members_monthly[-c(1,2)], col = "lightgrey",
        main = "CRUG Growth since inception", ylab="Percent")
```

Let's view the last 4 years.

```{r}
members_3_years <- 100*diff(members_monthly["2015-05/"]) / members_monthly["2015-05/"]
barplot(members_3_years, col = "lightgrey", main = "CRUG Growth, last 4 years", ylab="Percent")
```

Consider seasonal variation.

```{r}
month_percent_growth <- c(NA, NA, NA, NA, 100*diff(log(coredata(members_monthly))), NA, NA, NA, NA, NA, NA, NA)
seasonal_matrix <- matrix(month_percent_growth, ncol = 12, byrow = TRUE)
colnames(seasonal_matrix) <- month.abb
rownames(seasonal_matrix) <- 2010:2019
seasonal_matrix <- rbind(seasonal_matrix, Median=round(apply(seasonal_matrix, 2, median, na.rm=TRUE), 2))

kable(seasonal_matrix, digits=2, caption = "Percentage Growth per Month")
```

As one of the largest and oldest `R` user groups in existence, the Chicago `R` User Group has matured into a comfortable period of value. Growth rates are lower by percentage, but the group continues to serve a steady group of new use`R`s.
