---
title: "New Meetup Members"
author: "Justin M. Shea"
date: "April 21, 2018"
output: html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{New Meetup Members}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)

library(RUGtools)
```

## Introduction



## R User Group Introduction Slides template

This is a traditional ioslides R Markdown template, but modified to contain default content routinely used when introducing Chicago R user group meetups.
Slides are useful because they look good and you won't forget to do important things
like **thanking the sponsors!** Slides can be accessed from within R Studio 
using the `New R Markdown` dialog menu, and then selecting `From Template`. 
One can also use the `draft` function, exemplified below.

```{r, eval=FALSE}
rmarkdown::draft(file="new_meetup.Rmd", template = "intro_slides", package="RUGtools")
```

## Estimate your pizza order

In Chicago, we think a lot about Pizza. And if one is involved in the local meetup 
culture, this is doubly so. At a recent meetup group (which inronically shared the same name as a pizza shape), I counted nearly 6 large pizzas left over. Struck by an
overwelming sorrow, I vowed that we shall never be part of such a tragedy. With a
few data points, the `pizza_estimate` function helps us estimate how many pizzas to order.

```{r}

pizzas <- pizza_estimate(registered = 140, pizza_diameter = 18, attend_rate = 0.60, 
               serving = 2, style = "thin")

kable(pizzas)
```

 
Channeling our ever-curious pizza scientist, _**it turns out**_ the 
"party cut" inherits a few very attractive properties when dividing multiple 
pizzas among **n** guests. Smaller pieces allow guests to more precisely 
estimate pizza consumption, thus decreasing the integer-programming problem 
exacerbated by larger slices. 

```{r}
plot(5*c(1,0,-1,0), 5*c(0,1,0,-1) ,col="transparent",
     xaxs="i", yaxs="i", xaxt="n", yaxt="n", ylab="", xlab="") 

abline(h=-5:5); abline(v=-5:5)

polygon(4.3*sin(seq(0,2*pi,length=100)), 
        4.3*cos(seq(0,2*pi,length=100)))

text( x=c( (1:4)-2.5,(1:6)-3.5, (1:8)-4.5, (1:8)-4.5,
           (1:8)-4.5, (1:8)-4.5,  (1:6)-3.5, (1:4)-2.5 ),
      y=c( rep(4,4), rep(3,6), rep(2,8), rep(1,8), 
           rep(0,8), rep(-1,8), rep(-2,6), rep(-3,4) )-0.5, 
      labels=1:52)
```
 
By requesting the "party cut", one reduces wasted pizza and exhibits great stewardship of the sponsor resources entrusted to them.

## Data and Analysis

Chicago R User Group data is included and downloaded from meetup.com/ChicagoRUG.
Personally identifiable information has been removed, data formated and ready for analysis.

###  How many members joined since January of 2017?  
 
Load the member list data.

```{r}
data(member_list)
```

Lets plot it!

```{r}
plot(y = member_list$Count.Index, x = member_list$Joined.Group.on, type = "l", col = "blue",
     main = "Cumulative CRUG members",  
         ylab = "Members", xlab = "")
```

### How many joined since January 2017?

```{r}
members_2017_present <- subset(member_list, Joined.Group.on > "2017-01-01")

max(members_2017_present$Count.Index) - min(members_2017_present$Count.Index)

```


###  How many joined between meetups? 

First, get a unique ordered list of Meetup dates

```{r}
Meetup_dates <- sort(unique(member_list$Last.Attended))

new_members <- subset(member_list, Joined.Group.on > Meetup_dates[NROW(Meetup_dates)])

NROW(new_members)
```
 
How about the number of new members between last meetup and the one prior to that?

```{r}
new_members2 <- subset(member_list, Joined.Group.on <= Meetup_dates[NROW(Meetup_dates)] &
                                    Joined.Group.on > Meetup_dates[NROW(Meetup_dates)-1])

NROW(new_members2)
```


Since was getting repetitive, we've created a function `new_mem_counter` to count the number of new members joined between meetups.

```{r}
new_members <- new_mem_counter(member_list)

kable(new_members, align = 'l')
```

Lets Explore the `new_members` data set.
Which gap between meetups had the most new members?
 
```{r}
max_new_members <- new_members[new_members$New==max(new_members$New),]

kable(max_new_members, align = 'l')
```

Plot the `new members` data.

```{r}
   # Create Date Range Index
  Start_Date <- "2010-01-01"
    End_Date <- Sys.Date()
  Date_Index <- as.numeric(row.names(new_members[new_members$Date > Start_Date &
                                                new_members$Date <= End_Date,]))
  
  # Create x-axis labels, using year-month date format
  x_labels <- format(new_members$Date[Date_Index], "%Y-%m")

  # Plot
  barplot(new_members$New[Date_Index], names.arg = x_labels,
         main = "CRUG members, joined between meetups",  
         ylab = "New Members", xlab = "")
```

Plot the `new members` data since 2017.

```{r}
   # Create Date Range Index
  Start_Date <- "2017-01-01"
    End_Date <- Sys.Date()
  Date_Index <- as.numeric(row.names(new_members[new_members$Date > Start_Date &
                                                new_members$Date <= End_Date,]))
  
  # Create x-axis labels, using year-month date format
  x_labels <- format(new_members$Date[Date_Index], "%Y-%m")

  # Plot
  barplot(new_members$New[Date_Index], names.arg = x_labels, las=2,
         main = "CRUG members, joined between meetups",  
         ylab = "New Members", xlab = "")
```
 